### 2021-11-23 documentos/pce.tex
quito cosas de decoherencia de un qubit

% }}}
\subsection{Single qubit case} % {{{
\label{sec:single:qubit}
\todo{David escribe una primera version y luego Carlos itera}
\pce{} maps are defined as those valid quantum channels that \textit{nullify} \textit{Pauli strings} \ddnote{aqui introduzco el nombre estandar}, in the case of one qubit, they consist of maps nullifying the averages $r_\alpha:=\langle \sigma_\alpha \rangle$ with $\alpha=1,2,3$. The three components $r_\alpha$ form the well-known \textit{Bloch vector} $\vec r$, describing one qubit density matrices,
\begin{equation}
\rho=\frac{\one +\vec r \cdot \vec \sigma}{2}.
\end{equation}
Therefore, maps erasing components of $\vec r$ are parametrized in the following way,
\begin{equation}
r_\alpha \mapsto \tau_\alpha r_\alpha
\end{equation}
where $\tau_k$ is either $1$ or $0$. It is well-known that not every operation like this is a quantum map, for example collapsing the entire Bloch ball into a disk of radio equal to one is not a quantum channel. A direct evaluation of the complete positivity conditions~\cite{zimansbook,davalosdivisibility},
\begin{align}
1+\tau_1+\tau_2+\tau_3 &\geq 0 \nonumber \\
1+\tau_i-\tau_j-\tau_k &\geq 0 \ \ \forall i\neq j \neq k,
\end{align}
show that only five operations are \pce: the identity map, the completely depolarizing channel ($\rho \mapsto \one/2$); and bit, phase, and bit-phase flip channels~\cite{chuangbook}. These channels can be pictured with one column tables, see~\fref{fig:one:qubit:examples}. Finally notice that the condition $\tau_0=1$ is needed to have trace-preserving maps.
These operations have been studied in \cite{Ziman2005,davalosdivisibility} and are by definition diagonal in the Pauli basis $1/\sqrt{2} \left\{ \one, \sigma_x,\sigma_y,\sigma_z \right\}$, \ie{} $\hat \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$. They form a tetrahedron in the space of eigenvalues

with
\begin{equation}
\mcL_\alpha[\Delta]:= \frac{\gamma}{2}\left( \sigma_\alpha \Delta \sigma_\alpha -\Delta \right).
\label{eq:1qubit_semigroup}
\end{equation}
We will show later that this can be trivially generalized to the $N$ qubit case.

\begin{align}
U_\alpha\ket{\psi} \ket{0}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}+\sigma_\alpha \ket{\psi}\ket{1} \right)\\
U_\alpha\ket{\psi} \ket{1}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}-\sigma_\alpha \ket{\psi}\ket{1} \right)
\label{eq:1qubit_stinespring}
\end{align}
similar to the semigroup generator, we will show later that this can be trivially generalized to the $N$ qubit case.

\begin{itemize}
\item The single qubit case, describe some of the features.
\item Single qubit Kraus operators.
\item Single qubit relation with decoherence. 
\end{itemize}
% }}}
\subsection{Pauli component erasing maps} % {{{

@@

$r_1$ and thus does not correspond to a quantum operation.}

>>>>

% }}}
\subsection{Single qubit case} % {{{
\label{sec:single:qubit}
\todo{David escribe una primera version y luego Carlos itera}
\pce{} maps are defined as those valid quantum channels that \textit{nullify} \textit{Pauli strings} \ddnote{aqui introduzco el nombre estandar}, in the case of one qubit, they consist of maps nullifying the averages $r_\alpha:=\langle \sigma_\alpha \rangle$ with $\alpha=1,2,3$. The three components $r_\alpha$ form the well-known \textit{Bloch vector} $\vec r$, describing one qubit density matrices,
\begin{equation}
\rho=\frac{\one +\vec r \cdot \vec \sigma}{2}.
\end{equation}
Therefore, maps erasing components of $\vec r$ are parametrized in the following way,
\begin{equation}
r_\alpha \mapsto \tau_\alpha r_\alpha
\end{equation}
where $\tau_k$ is either $1$ or $0$. It is well-known that not every operation like this is a quantum map, for example collapsing the entire Bloch ball into a disk of radio equal to one is not a quantum channel. A direct evaluation of the complete positivity conditions~\cite{zimansbook,davalosdivisibility},
\begin{align}
1+\tau_1+\tau_2+\tau_3 &\geq 0 \nonumber \\
1+\tau_i-\tau_j-\tau_k &\geq 0 \ \ \forall i\neq j \neq k,
\end{align}
show that only five operations are \pce: the identity map, the completely depolarizing channel ($\rho \mapsto \one/2$); and bit, phase, and bit-phase flip channels~\cite{chuangbook}. These channels can be pictured with one column tables, see~\fref{fig:one:qubit:examples}. Finally notice that the condition $\tau_0=1$ is needed to have trace-preserving maps.
These operations have been studied in \cite{Ziman2005,davalosdivisibility} and are by definition diagonal in the Pauli basis $1/\sqrt{2} \left\{ \one, \sigma_x,\sigma_y,\sigma_z \right\}$, \ie{} $\hat \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$. They form a tetrahedron in the space of eigenvalues 
% }}}
\subsection{Pauli component erasing maps} % {{{

@@

$r_1$, collapsing the Block sphere into a disk, and thus does not correspond to a quantum operation.}
